### 2021-10-25 paper/output/document/paper41.tex
finished application tests

While Kitcher's conception of a maxim captures Kant's idea of acting for duty's own sake, I will not implement it 
because it is not necessary for putting maxims through the FUL. Indeed, Kitcher acknowledges that 
O'Neill's formulation suffices for the universalizability test, but is not the general notion of a maxim.
In order to pass the maxim through the FUL, it suffices to know the circumstance, act, and goal. The FUL
derives the motive that Kitcher bundles into the maxim, so automating the FUL does not require 
including a motive. The ``input" to the FUL is the circumstance, act, goal tuple. My project takes 
this input and returns the motivation that the dutiful, moral agent would adopt. Additionally, doing
justice to the rich notion of motive requires modelling the operation of practical reason itself, 
which is outside the scope of this project. My work focuses on the universalizability test, but future work that 
models the process of practical reason may use my implementation of the FUL as a ``library." Combined 
with a logic of practical reason, an implementation of the FUL can move from evaluating a maxim to 
evaluating an agent's behavior, since that's when ``acting from duty" starts to matter.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ will\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim\ {\isasymRightarrow}\ s{\isasymRightarrow}\ \ t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}W\ {\isacharunderscore}\ {\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}will\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isachardot}\ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}a\ s{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
\isacommand{print{\isacharunderscore}theorems}\isamarkupfalse%
%
\begin{isamarkuptext}%
Korsgaard claims that ``to will an end, rather than just
wishing for it or wanting it, is to set yourself to be its cause" \cite[38]{sources}. To will a maxim
is to set yourself to be the cause of its goal by taking the means 
specified in the maxim in the relevant circumstances. This coheres with 
Kitcher's and Korsgaard's understanding of a maxim as a principle or rule to live by.

@@

If the circumstances do not hold and the goal is achieved, then the maxim is vacuously effective, since 
it is vacuously willed (as described above). While this scenario is counterintuitive, it is not very 
interesting for my purposes because, when the circumstances do not hold, a maxim is not applicable. It 
doesn't really make sense to evaluate a maxim when it's not supposed to be applied. The maxim ``When on Jupiter,
read a book to one-up your nemesis" is vacuously effective because it can never be disproven.%
\ universalized{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}t{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}universalized\ {\isasymequiv}\ {\isasymlambda}M\ s{\isachardot}\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ W\ M\ p\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
\ not{\isacharunderscore}universalizable\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}not{\isacharunderscore}universalizable\ {\isasymequiv}\ {\isasymlambda}M\ s{\isachardot}\ {\isacharparenleft}{\isasymTurnstile}\ {\isacharparenleft}universalized\ M\ s\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}E\ M\ s{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
\isamarkupcmt{The maxim willed by subject $s$ is not universalizable if, for all people $p$, if $p$ wills M, then 
$M$ is no longer effective for $s$.%
As before, the concepts of prohibition and permissibility will be helpful here. The unit of 
evaluation for my formalization of the FUL is the act of willing a maxim, which entails performing 
the maxim's act in the relevant circumstances. Therefore, I will say that, just as the act of willing a
 maxim can be obligatory for a subject, it can be prohibited or permissible for a subject.\footnote{In 
the rest of this section, for convenience, I will use the phrase ``subject s willing maxim M is obligatory" 
interchangeably with ``maxim M is obligatory for subject s." I will use ``maxim M is obligatory" to 
refer to M being obligatory for any arbitrary subject, which I will show to be equivalent to M being 
obligatory for a specific subject.}%
\ prohibited{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}t{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}prohibited\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isachardot}\ O{\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}will\ {\isacharparenleft}c{\isacharcomma}a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ {\isacharbar}\ c{\isacharbraceright}{\isachardoublequoteclose}\isanewline
\ permissible{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}t{\isachardoublequoteclose}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}permissible\ {\isasymequiv}\ {\isasymlambda}M\ s{\isachardot}\ \isactrlbold {\isasymnot}\ {\isacharparenleft}prohibited\ M\ s{\isacharparenright}{\isachardoublequoteclose}\isanewline
\isamarkupcmt{I will say that a maxim is permissible for a subject if it is not prohibited for that subject to 
will that maxim.%
One problem with prior formalization of the categorical imperative was that they didn't
prohibit contradictory obligations, partially because DDL itself allows contradictory obligations. 
Kant subscribes to the general, popular view that morality is supposed to guide action, so ought implies 
can\footnote{Kohl points out that this principle is referred to as 
Kant's dictum or Kant's law in the literature. \cite[footnote 1]{kohl}}. Kohl reconstructs his argument for the principle as 
follows: if the will cannot comply with the moral law, then the moral law has no prescriptive authority 
for the will \cite[703-4]{kohl}. This defeats the purpose of Kant's theory—to develop an unconditional, categorical imperative 
for rational agents. Ought implies can requires that obligations never contradict, because an agent 
can't perform contradictory actions. Therefore, any ethical theory that respects ought implies can, 
and Kantian ethics in particular, must not result in conflicting obligations.

@@

\ O{\isacharunderscore}diamond\ \isanewline

@@

\ prod{\isachardot}simps{\isacharparenleft}{\isadigit{2}}{\isacharparenright}\ split{\isacharunderscore}conv\ \isacommand{by}\isamarkupfalse%

@@

To get around this, I will exclude what I call ``badly formed maxims," which are those maxims such that the goal has already been 
achieved or the act has already been acted on. Under my formalization, such maxims are 
not well-formed. To understand why, I return to Korsgaard's and O'Neill's interpretations of a maxim as a practical
guide to action. A maxim is a practical principle that guides how we behave in everyday life. A 
principle of the form ``When you are eating breakfast, eat breakfast in order to eat breakfast," is not 
practically relevant. No agent would ever need to act on such a principle. It is not contradictory
or prohibited, but it is the wrong kind of question to be asking. It is not a 
well-formed maxim, so the categorical imperative does not apply to it. (more explanation in philosophical 
writing collection)%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ well{\isacharunderscore}formed{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}i{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}well{\isacharunderscore}formed\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ w{\isachardot}\ {\isacharparenleft}{\isasymnot}\ {\isacharparenleft}\ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ g{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}\ {\isasymand}\ {\isacharparenleft}{\isasymnot}\ {\isacharparenleft}\ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ a\ s{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{This abbreviation formalizes the well-formedness of a maxim for a subject. The goal cannot be 
already achieved in the circumstances and the subject cannot have already performed the act.%
}\isanewline
\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ FUL\ \isakeyword{where}\ {\isachardoublequoteopen}FUL\ {\isasymequiv}\ {\isasymforall}M{\isacharcolon}{\isacharcolon}maxim{\isachardot}\ {\isasymforall}s{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isacharparenleft}{\isasymforall}w{\isachardot}\ well{\isacharunderscore}formed\ M\ s\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}not{\isacharunderscore}universalizable\ M\ s\ {\isasymlongrightarrow}\ {\isasymTurnstile}\ prohibited\ M\ s\ {\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{Let's try the exact same formalization of the FUL as above, except that it only applies to 
maxims that are well-formed at every world.%
}\isanewline
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}FUL{\isachardoublequoteclose}\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}true{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{The FUL does not hold in DDL, because nitpick is able to find a model for my system in which it is 
false. If the FUL were already a theorem of the system, adding it wouldn't make the system any more 
powerful, so this is the desired result.

@@

The logic confirmed that certain kinds
of circumstance, act, goal tuples are too badly formed for the categorical imperative to logically 
apply to them. The realization of this subtle problem would have been incredibly difficult without 
computational tools. The syntax and typing of Isabelle/HOL forced me to bind the free-variable $M$
in the FUL in different ways and allowed me to quickly test many bindings. The discovery of this 
logical inconsistency then enabled a philosophical insight about which kinds of maxims make sense as 
practical principles. This is one way to do computational ethics: model a system in a logic, use 
computational tools to refine and debug the logic, and then use insights about the logic to derive 
insights about the ethical phenonema it is modelling. This procedure parallels the use of proofs in 
theoretical math to understand the mathematical objects they model.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
One potential problem with my formalization is that it does not use the modal nature of the system. 
All of the properties that the FUL investigates hold at all worlds, in effect removing the modal nature 
of the system. This approach simplifies logical and therefore computational complexity, improving 
performance. On the other hand, it doesn't use the full expressivity of DDL. If I run into problems 
later on, one option is to tweak the FUL to use this expressivity.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Application Tests%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
As with the naive formalization and Kroy's formalization, I will apply my testing framework to 
my custom formalization of the FUL. I will begin with some basic application tests. In these tests, 
I specify particular maxims as constants with no properties and gradually add properties to understand 
how the system handles different kinds of maxims.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Metaethical Tests%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Recall that metaethical tests test formal properties of the system that apply to any maxim, not 
just those specified in the application tests. In this section I adapt the metaethical tests developed 
in previous sections to my formalization of the categorical imperative. I preserved the philosophical 
goal of each test but modified them to test the stronger, richer notion of a maxim.

>>>>

While Kitcher's conception of a maxim captures Kant's idea of acting for duty's own sake, I will not implement it 
because it is not necessary for putting maxims through the FUL. Indeed, Kitcher acknowledges that 
O'Neill's formulation suffices for the universalizability test, but is not the general notion of a maxim.
In order to pass the maxim through the FUL, it suffices to know the circumstance, act, and goal. The FUL
derives the motive that Kitcher bundles into the maxim, so automating the FUL does not require 
including a motive. The ``input" to the FUL is the circumstance, act, goal tuple. My project takes 
this input and returns the motivation that the dutiful, moral agent would adopt. Additionally, doing
justice to the rich notion of motive requires modelling the operation of practical reason itself, 
which is outside the scope of this project. My work focuses on the universalizability test, but future work that 
models the process of practical reason may use my implementation of the FUL as a ``library." Combined 
with a logic of practical reason, an implementation of the FUL can move from evaluating a maxim to 
evaluating an agent's behavior, since that's when ``acting from duty" starts to matter.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ will\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim\ {\isasymRightarrow}\ s{\isasymRightarrow}\ \ t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}W\ {\isacharunderscore}\ {\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}will\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isachardot}\ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}a\ s{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
\begin{isamarkuptext}%
Korsgaard claims that ``to will an end, rather than just
wishing for it or wanting it, is to set yourself to be its cause" \cite[38]{sources}. To will a maxim
is to set yourself to be the cause of its goal by taking the means 
specified in the maxim in the relevant circumstances. This coheres with 
Kitcher's and Korsgaard's understanding of a maxim as a principle or rule to live by.

@@

If the circumstances do not hold and the goal is achieved, then the maxim is vacuously effective, since 
it is vacuously willed (as described above). While this scenario is counterintuitive, it is not very 
interesting for my purposes because, when the circumstances do not hold, a maxim is not applicable. It 
doesn't really make sense to evaluate a maxim when it's not supposed to be applied. The maxim ``When on Jupiter,
read a book to one-up your nemesis" is vacuously effective because it can never be disproven.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ universalized{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}t{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}universalized\ {\isasymequiv}\ {\isasymlambda}M{\isachardot}\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ {\isacharparenleft}W\ M\ p{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ holds{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}t{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}holds\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}{\isachardot}\ c{\isachardoublequoteclose}\isanewline
\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ not{\isacharunderscore}universalizable\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}not{\isacharunderscore}universalizable\ {\isasymequiv}\ {\isasymlambda}M\ s{\isachardot}\ {\isasymforall}w{\isachardot}\ {\isacharparenleft}{\isacharparenleft}universalized\ M{\isacharparenright}\ \ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}E\ M\ s{\isacharparenright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{The formula above reads ``at world $w$, if M is universalized and M is acted on (i.e. the circumstances 
of M hold), then M is not effective."

Notice that the antecedent specifies that the circumstances hold at the given world. 
When evaluating if a maxim is universalizable or not, we want to ignore worlds where the circumstance 
do not hold. At these worlds, the maxim is trivially effective and thus trivially universalizable. If we didn't exclude such worlds from 
consideration, a maxim with circumstances that ever fail to hold would be universalizable. Clearly 
this is not a desirable conclusion, since maxims like ``When you need money, lie to get easy money"
would be universalizable.%
}%
\begin{isamarkuptext}%
As before, the concepts of prohibition and permissibility will be helpful here. The unit of 
evaluation for my formalization of the FUL is the act of willing a maxim, which entails performing 
the maxim's act in the relevant circumstances. Therefore, I will say that, just as the act of willing a
 maxim can be obligatory for a subject, it can be prohibited or permissible for a subject.\footnote{In 
the rest of this section, for convenience, I will use the phrase ``subject s willing maxim M is obligatory" 
interchangeably with ``maxim M is obligatory for subject s." I will use ``maxim M is obligatory" to 
refer to M being obligatory for any arbitrary subject, which I will show to be equivalent to M being 
obligatory for a specific subject.}%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ prohibited{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}t{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}prohibited\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isachardot}\ O{\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}will\ {\isacharparenleft}c{\isacharcomma}a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ {\isacharbar}\ c{\isacharbraceright}{\isachardoublequoteclose}\isanewline
\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ permissible{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}t{\isachardoublequoteclose}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}permissible\ {\isasymequiv}\ {\isasymlambda}M\ s{\isachardot}\ \isactrlbold {\isasymnot}\ {\isacharparenleft}prohibited\ M\ s{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{I will say that a maxim is permissible for a subject if it is not prohibited for that subject to 
will that maxim.%
}%
\begin{isamarkuptext}%
One problem with prior formalizations of the categorical imperative was that they didn't
prohibit contradictory obligations, partially because DDL itself allows contradictory obligations. 
Kant subscribes to the general, popular view that morality is supposed to guide action, so ought implies 
can\footnote{Kohl points out that this principle is referred to as 
Kant's dictum or Kant's law in the literature. \cite[footnote 1]{kohl}}. Kohl reconstructs his argument for the principle as 
follows: if the will cannot comply with the moral law, then the moral law has no prescriptive authority 
for the will \cite[703-4]{kohl}. This defeats the purpose of Kant's theory—to develop an unconditional, categorical imperative 
for rational agents. Ought implies can requires that obligations never contradict, because an agent 
can't perform contradictory actions. Therefore, any ethical theory that respects ought implies can, 
and Kantian ethics in particular, must not result in conflicting obligations.

@@

\ O{\isacharunderscore}diamond\isanewline

@@

\ case{\isacharunderscore}prod{\isacharunderscore}conv\ no{\isacharunderscore}contradictions\ old{\isachardot}prod{\isachardot}case\ old{\isachardot}prod{\isachardot}case\ \isacommand{by}\isamarkupfalse%

@@

To get around this, I will exclude what I call ``badly formed maxims," which are those maxims such that the goal has already been 
achieved or the act has already been acted on. Under my formalization, such maxims are 
not well-formed. To understand why, I return to Korsgaard's and O'Neill's interpretations of a maxim as a practical
guide to action. A maxim is a practical principle that guides how we behave in everyday life. A 
principle of the form ``When you are eating breakfast, eat breakfast in order to eat breakfast," is not 
practically relevant. No agent would ever need to act on such a principle. It is not contradictory
or prohibited, but it is the wrong kind of question to be asking. It is not a 
well-formed maxim, so the categorical imperative does not apply to it. (more explanation in philosophical 
writing collection)%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ well{\isacharunderscore}formed{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}i{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}well{\isacharunderscore}formed\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}{\isachardot}\ {\isasymlambda}s{\isachardot}\ {\isasymlambda}w{\isachardot}\ {\isacharparenleft}{\isasymnot}\ \ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ g{\isacharparenright}\ w{\isacharparenright}\ {\isasymand}\ {\isacharparenleft}{\isasymnot}\ \ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ a\ s{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{This abbreviation formalizes the well-formedness of a maxim for a subject. The goal cannot be 
already achieved in the circumstances and the subject cannot have already performed the act.%
}\isanewline
\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ FUL\ \isakeyword{where}\ {\isachardoublequoteopen}FUL\ {\isasymequiv}\ {\isasymforall}M{\isacharcolon}{\isacharcolon}maxim{\isachardot}\ {\isasymforall}s{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isacharparenleft}{\isasymforall}w{\isachardot}\ well{\isacharunderscore}formed\ M\ s\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}not{\isacharunderscore}universalizable\ M\ s\ {\isasymlongrightarrow}\ {\isasymTurnstile}\ {\isacharparenleft}prohibited\ M\ s{\isacharparenright}\ {\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{Let's try the exact same formalization of the FUL as above, except that it only applies to 
maxims that are well-formed at every world.%
}\isanewline
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}FUL{\isachardoublequoteclose}\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}true{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{The FUL does not hold in DDL, because nitpick is able to find a model for my system in which it is 
false. If the FUL were already a theorem of the system, adding it wouldn't make the system any more 
powerful, so this is the desired result.

@@

The logic confirmed that certain kinds
of circumstance, act, goal tuples are too badly formed for the categorical imperative to logically 
apply to them. The realization of this subtle problem would have been incredibly difficult without 
computational tools. The syntax and typing of Isabelle/HOL forced me to bind the free-variable $M$
in the FUL in different ways and allowed me to quickly test many bindings. The discovery of this 
logical inconsistency then enabled a philosophical insight about which kinds of maxims make sense as 
practical principles. This is one way to do computational ethics: model a system in a logic, use 
computational tools to refine and debug the logic, and then use insights about the logic to derive 
insights about the ethical phenonema it is modelling. This procedure parallels the use of proofs in 
theoretical math to understand the mathematical objects they model.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
One potential problem with my formalization is that it does not use the modal nature of the system. 
All of the properties that the FUL investigates hold at all worlds, in effect removing the modal nature 
of the system. This approach simplifies logical and therefore computational complexity, improving 
performance. On the other hand, it doesn't use the full expressivity of DDL. If I run into problems 
later on, one option is to tweak the FUL to use this expressivity.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Application Tests%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
As with the naive formalization and Kroy's formalization, I will apply my testing framework to 
my custom formalization of the FUL. I will begin with some basic application tests. In these tests, 
I specify particular maxims as constants with no properties and gradually add properties to understand 
how the system handles different kinds of maxims.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
I will show that the maxim, ``When strapped for cash, falsely promise to pay your friend back
to get some easy money." is prohibited. This example is due to Korsgaard and she uses it to highlight 
the strength of her preferred interpretation of the FUL, the practical contradiction interpretation \cite{KorsgaardFUL}.
There are two possible readings of this maxim, and I will show that my formalization can handle both. 
Under the first reading, the act of falsely promising is read as
as entering a pre-existing, implicit, social system of promising with no intention of upholding your 
promise. Under the second reading, the act of falsely promising is equivalent to uttering the worlds 
``I promise X" without intending to do X. The differences between these readings lies in the difference 
between promising as an act with meaning in a larger social structure and the utterance ``I promise."

Under the first reading, the maxim fails because falsely promising is no longer possible in a world where 
everyone everyone does so. This is how the logical contradiction interpretation reads this maxim—falsely 
promising is no longer possible when universalized because the institution of promising breaks down. 
The practical contradiction view also prohibits this maxim because if falsely promising is not longer 
possible, then it is no longer an effective way to achieve the end of getting some money. Below I 
define some logical tools to formalize this reading of this maxim.%
\isacommand{consts}\isamarkupfalse%
\ when{\isacharunderscore}strapped{\isacharunderscore}for{\isacharunderscore}cash{\isacharcolon}{\isacharcolon}t\isanewline
\isamarkupcmt{Constant representing the circumstances ``when strapped for cash." Recall that the type of circumstances 
is a term because circumstances can be true or false at a world.%
\isacommand{consts}\isamarkupfalse%
\ falsely{\isacharunderscore}promise{\isacharcolon}{\isacharcolon}os\isanewline
\isamarkupcmt{Constant representing the act ``make a false promise to pay a loan back." Recall that the type of
an act is an open sentence because the sentence ``subject s performs act a" can be true or false at a world.%
\isacommand{consts}\isamarkupfalse%
\ to{\isacharunderscore}get{\isacharunderscore}easy{\isacharunderscore}cash{\isacharcolon}{\isacharcolon}t\isanewline
\isamarkupcmt{Constant representing the goal ``to get some money." Recall that the type of a goal 
is a term because a goal can be true or false at a world depending on whether it is achieved or not.%
\ false{\isacharunderscore}promising{\isacharcolon}{\isacharcolon}maxim\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}false{\isacharunderscore}promising\ {\isasymequiv}\ {\isacharparenleft}when{\isacharunderscore}strapped{\isacharunderscore}for{\isacharunderscore}cash{\isacharcomma}\ falsely{\isacharunderscore}promise{\isacharcomma}\ to{\isacharunderscore}get{\isacharunderscore}easy{\isacharunderscore}cash{\isacharparenright}{\isachardoublequoteclose}\isanewline
\isamarkupcmt{Armed with the circumstances, act, and goal above, I can define the example maxim as a tuple.%
The logical objects above are ``empty," in the sense that I haven't specified any of their 
relevant properties. I will define these properties as assumptions and will show that, if the maxim 
above satisfies the assumed properties, it is prohibited.%
\ everyone{\isacharunderscore}can{\isacharprime}t{\isacharunderscore}lie\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}everyone{\isacharunderscore}can{\isacharprime}t{\isacharunderscore}lie\ {\isasymequiv}\ {\isasymforall}w{\isachardot}\ {\isasymnot}\ {\isacharparenleft}{\isasymforall}s{\isachardot}\ falsely{\isacharunderscore}promise{\isacharparenleft}s{\isacharparenright}\ w{\isacharparenright}\ {\isachardoublequoteclose}\isanewline
\isamarkupcmt{Under this reading, the problem with this maxim is that everyone can't
falsely promise simultaneously because the institution of promising will break down. It's probably 
possible to say something stronger than this (i.e. that if enough but not necessarily all people
falsely promise promising is no longer possible), but for my purposes this will suffice. The above 
formula reads, ``At all worlds, it is not the case that everyone falsely promises."%
\ circumstances{\isacharunderscore}hold\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}circumstances{\isacharunderscore}hold\ {\isasymequiv}\ {\isasymforall}w{\isachardot}\ when{\isacharunderscore}strapped{\isacharunderscore}for{\isacharunderscore}cash\ w{\isachardoublequoteclose}\isanewline
\isamarkupcmt{This assumption narrows our scope of consideration to worlds where the circumstances of 
being strapped for cash hold. This is important because, at worlds where the circumstances do not hold, 
a maxim is trivially effective (since it's never acted on) and thus trivially universalizable. This 
assumption also makes practical sense; when evaluating a maxim, an agent would care about it specifically
at worlds where the circumstances hold, since these are the worlds where the maxim actually prescribes action.%
\ example{\isacharunderscore}is{\isacharunderscore}well{\isacharunderscore}formed\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}example{\isacharunderscore}is{\isacharunderscore}well{\isacharunderscore}formed\ {\isasymequiv}\ {\isasymforall}s{\isachardot}\ {\isasymTurnstile}\ {\isacharparenleft}well{\isacharunderscore}formed\ false{\isacharunderscore}promising\ s{\isacharparenright}{\isachardoublequoteclose}\isanewline
\isamarkupcmt{This assumption states that the maxim of falsely promising is well-formed. This breaks down into
two individual assumptions. First, being strapped for cash can't imply falsely promising, which is plausible
because many people won't falsely promise under conditions of poverty. Second, being strapped for cash
can't imply getting ready cash, which is also plausible because people often fail to secure cash even 
when they need it.%
Putting it all together, I want to show that if the three assumptions justified above hold, then 
the constructed maxim is prohibited. Below is the proof%
\ lying{\isacharunderscore}bad{\isacharunderscore}{\isadigit{1}}{\isacharcolon}\isanewline
\ \ \isakeyword{assumes}\ everyone{\isacharunderscore}can{\isacharprime}t{\isacharunderscore}lie\isanewline
\ \ \isakeyword{assumes}\ circumstances{\isacharunderscore}hold\isanewline
\ \ \isakeyword{assumes}\ example{\isacharunderscore}is{\isacharunderscore}well{\isacharunderscore}formed\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}s{\isachardot}\ {\isasymTurnstile}\ {\isacharparenleft}prohibited\ false{\isacharunderscore}promising\ s{\isacharparenright}{\isachardoublequoteclose}\isanewline
\isacommand{proof}\isamarkupfalse%
{\isacharminus}\isanewline
\ \ \isacommand{have}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isasymforall}s{\isachardot}\ not{\isacharunderscore}universalizable\ false{\isacharunderscore}promising\ s{\isachardoublequoteclose}\isanewline
\ \ \ \ \isacommand{by}\isamarkupfalse%
\ {\isacharparenleft}simp\ add{\isacharcolon}\ assms{\isacharparenleft}{\isadigit{1}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{2}}{\isacharparenright}{\isacharparenright}\isanewline
\isamarkupcmt{I manually broke the proof into this intermediate lemma and the conclusion, and then Sledgehammer 
automatically found a proof.%
\ \ \isacommand{thus}\isamarkupfalse%
\ {\isacharquery}thesis\isanewline
\ \ \ \ \isacommand{using}\isamarkupfalse%
\ FUL\ assms{\isacharparenleft}{\isadigit{3}}{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
\ blast\ \isanewline
\isacommand{qed}\isamarkupfalse%
Under the second reading of this maxim, the act ``falsely promising" refers to uttering the 
sentence ``I promise to do X" with no intention of actually doing X\footnote{Note that under this 
reading, the maxim isn't prohibited under the logical contradiction interpretation because making an 
utterance is still possible even if eveyrone else makes that utterance. I will discuss this in detail 
later in this section in the context of the difference between natural and conventional acts.}. 
Under this reading, the practical contradiction interpretation prohibits this maxim because, in a world 
